LaMachine: A meta-distribution for NLP software

### 2018-07-26 docs/lamachine_extabstract_clarin2018.tex
[paper] clarified 'upstream'

LaMachine we also aims to harmonise the metadata of all installed software, by converting metadata from upstream repositories to
the CodeMeta standard\footnote{\url{https://codemeta.github.io/}, described in JSON-LD} \cite{codemeta,codemetar} where possible, or encouraging software developers to provide
their own. This in turn enables other tools to do proper service discovery and provenance logging.

>>>>

LaMachine also aims to harmonise the metadata of all installed software, by converting metadata from upstream
repositories\footnote{i.e. repositories that where tool providers depositor their software} to
the CodeMeta standard\footnote{\url{https://codemeta.github.io/}, described in JSON-LD} \cite{codemeta,codemetar} where possible, or encouraging software developers to provide
their own. This in turn enables other tools to do proper service discovery and provenance logging.
